Reproducible Workflow on a Public Cloud for Computational Fluid Dynamics

### 2019-03-23 tex/MesnardoBarba2019.tex
Add 3D snake figures to manuscript

>>>>

\begin{figure}[!h]
    \centering
    \includegraphics[width=8cm]{figures/ux_uy_xz_plane.png}
    \caption{Filled contour of the streamwise velocity (top) and cross-flow velocity (bottom) behind the snake cylinder in the $x/z$ plane at $y/c=-0.2$ in the wake of the snake cylinder with a $35$-degree angle of attack at Reynolds number $2000$ after $100$ time-units of flow simulations. There are 52 contours from $-1.0$ to $1.0$. The grey area shows a projection of the snake cylinder in the $x/z$ plane. The solid black line defines the contour with $u_x = 0$ (top) and $u_y = 0$ (bottom).}
    \label{fig:ux_uy_xz_plane_3d}
\end{figure}

\begin{figure*}[!h]
    \centering
    \includegraphics[width=16cm]{figures/qcrit_wx_wake3d_0001.png}
    \caption{Lateral view of the isosurfaces of the Q-criterion ($Q = 1.0$) in the wake of the snake cylinder (with a $35$-degree angle of attack) at Reynolds number $2000$. The isosurfaces are colored with the streamwise vorticity ($-5 \leq w_x c / U_\infty \leq 5$).}
    \label{fig:qcrit_wx_3d}
\end{figure*}
